Supplementary Information

### 2021-03-23 doc/manuscript/ForestGEO_treerings_SI.Rmd
JLB feedback

We suspect that both of these factors may underlie the tendency for the traditional method to estimate stronger climate sensitivity than the approach developed here for Scotty Creek (Fig. `r SC_traditional_comparison`), a comprehensively sampled black spruce forest (i.e., including young trees) on melting permafrost. 
We note, however, that there were no statistically significant differences in the *beta* coefficients of the two approaches at this site.

@@

Our analysis included two sites where climate change has had pronounced effects on tree growth: Little Tesuque, New Mexico, USA (LT) and Scotty Creek, NW Territories, Canada (SC).
At LT, increasingly warm drought has dramatically reduced growth [@touchan_millennial_2011; @williams_temperature_2013], resulting in many missing rings in recent years.
At SC, rapidly rising temperatures are causing melting permafrost, summer moisture stress, resulting in negative growth trends in basal area index (BAI) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees [@sniderhan_growth_2016].

>>>>

We suspect that both of these factors may underlie the tendency for the traditional method to estimate stronger climate sensitivity than the approach developed here for Scotty Creek (Fig. `r SC_traditional_comparison`), a comprehensively sampled black spruce forest (i.e., including young trees) on thawing permafrost. 
We note, however, that there were no statistically significant differences in the *beta* coefficients of the two approaches at this site.

@@

Our analysis included two sites where climate change has had pronounced effects on tree growth: Little Tesuque, New Mexico, USA (LT) and Scotty Creek, NW Territories, Canada (SC).
At LT, increasingly warm drought has dramatically reduced growth [@touchan_millennial_2011; @williams_temperature_2013], resulting in many missing rings in recent years.
At SC, rapidly rising temperatures are causing permafrost thaw, summer moisture stress, resulting in negative growth trends in basal area index (BAI) starting around 1950 and significant growth declines since 1970 in `r round(249/(249+69+127)*100, digits=0)`% of trees [@sniderhan_growth_2016].
